Several limitations should be acknowledged.

First, the join is evaluated on real images only by a \emph{structural} connectivity
metric. Hand-drawn corpora annotate component boxes and wire strokes but not which
terminals are electrically common, so there is no net-level ground truth on real
images against which to certify that a recovered connection is the \emph{correct}
one. The synthetic harness supplies net-level truth by construction and shows the
completion does not reduce precision there, but a manually net-annotated real
benchmark remains important future work.

Second, the synthetic harness is only as faithful as its error model. The injected
perturbations (jitter, cut-short, dropped wires, wrong-pin snaps, anchor
displacement) are a first-pass approximation, not a model calibrated to the real
detector's measured failure distribution. Synthetic join scores are therefore used
as robustness and regression signals, with the real benchmark remaining the
decisive setting; calibrating the error model to the detector is future work.

Third, the recovery has a residual cost. On the densest real layouts the
degree-budget completion can introduce a small number of two-terminal self-loops
(a component shorted onto one net). The one-edge-per-terminal budget and the
self-loop guard bound this effect rather than eliminating it, and it is the price
of the large reduction in floating terminals that drives the connectivity gain.

Fourth, the hardest detection failures remain recall-driven and concentrated in
dense drawings: four of the 134 evaluation images score wire F1 below 0.50, where
large component occlusion removes nearby wire endpoints, and crossover is the
weakest component class (70.7\% recall) because crossing wires are visually
ambiguous. The pipeline also remains dependent on accurate component priors, since
occlusion and region-of-interest selection are driven by the detector.

Fifth, the evaluation, although carefully annotated, draws from a single corpus of
134 images; generalization across further drawing styles and acquisition
conditions should be validated. Finally, only components with a known device model
(resistor, capacitor, inductor, voltage source, diode, transistor) are emitted to
SPICE; integrated circuits, op-amps, and similar parts are detected and placed in
the topology but skipped at the simulation stage, so circuits dominated by such
parts are only partially simulatable.
