CircuitDigitizer is organized as a transparent, stage-by-stage pipeline that takes
a photographed hand-drawn schematic and emits a SPICE netlist. Components are
localized by a trained oriented detector and used to guide preprocessing; wire
segments are extracted by a deterministic computer-vision stage; the
\emph{Degree-Budget Topology Join} converts detected wires and components into a
connected netlist; and the netlist is exported as SPICE. The full architecture is
shown in Fig.~\ref{fig:architecture}. The join is the central methodological
contribution and is described in its own subsection. Every stage is inspectable in
isolation, and no wire-specific training is required for the extraction or join
stages.

\subsection*{Datasets and evaluation set}

Component priors and the component detector were obtained from the CGHD-1152
hand-drawn circuit corpus, which provides oriented component annotations
\cite{Thoma2021}. The pipeline is evaluated on a set of 134 hand-drawn schematic
photographs for which both component annotations and manually verified wire
annotations are available (3{,}524 wire segments in total). Wire extraction is
scored with the repository metric: a detected segment is a true positive when its
endpoints fall within a 20~px mean tolerance of the nearest ground-truth segment,
and precision, recall, and F1 are reported. Because real schematics provide no
\emph{net-level} ground truth --- there is no annotation of which terminals are
electrically common --- the join is evaluated both by a structural connectivity
metric on the real set and by a synthetic ground-truth harness (described below)
that supplies net-level truth by construction.

\subsection*{Component detection}

Components are localized with an oriented-bounding-box detector
(YOLO26M-OBB \cite{UltralyticsYOLO}) trained on CGHD-1152. The original 61 symbol
classes were merged into 16 functional classes; this merging was the single most
important design choice and raised mean average precision from roughly 50\% to the
final 88.5\% mAP50 (78.3\% mAP50-95). The detector is the single source of truth
for component identity and location, replacing earlier reliance on pre-trained
third-party labels with non-standard class indices. Detection runs in
approximately one second per image on CPU.

\subsection*{Component-guided preprocessing}

Each detected component polygon is occluded by filling it with the local median
intensity estimated from a margin around the polygon (15\% of the bounding-box
size, minimum 5~px) \cite{Bradski2000}. This suppresses symbol strokes and printed
text that would otherwise be converted into spurious wire evidence, while leaving
junction points intact. The image is then cropped to the union of all component
boxes plus 10~px of padding, which removes scanner borders and paper edges; the
crop offset is tracked so that extracted endpoints can be mapped back to image
coordinates.

\subsection*{Wire extraction}

Wire evidence is produced by Sauvola adaptive thresholding \cite{Sauvola2000} in a
$67 \times 67$ window with $k = 0.285$, chosen because local adaptive thresholding
preserves thin foreground strokes on degraded document content far better than
global methods. The binary mask is closed with a $3 \times 3$ elliptical kernel,
labeled into connected components (minimum area 28~px), and each component is
reduced to a line segment whose endpoints are obtained by principal-component
analysis rather than by extremal pixels. Near-duplicate segments are removed by an
overlap test (angle $12^\circ$, distance 8~px), and an anchor filter
(endpoint distance 16~px, link distance 8~px) discards floating endpoints that do
not reach a component or another wire. No global line-merging or length-filtering
stage is used; both were found to destroy true positives.

\subsection*{The Degree-Budget Topology Join}

The join converts the extracted wires and detected components into electrical
nodes. It proceeds in two phases: an endpoint-graph base join, followed by a
degree-budget completion that recovers the connections lost when the detector
drops or truncates a wire.

\paragraph{Phase 1 --- endpoint-graph base.}
Component pins are derived from each oriented box (two terminals on the short-axis
midpoints for two-terminal parts, class-specific layouts otherwise), and wires are
extended 12~px along their direction to close occlusion gaps. Wire endpoints and
pins are treated as nodes of a single graph and merged by union-find under three
edge types: a wire body links its own two endpoints; two endpoints within a
scale-relative tolerance $\tau_{\mathrm{join}}$ are joined (fragments, corners);
and an endpoint binds the pin it points at, assigned component-first --- the
endpoint is attached to the nearest component by bounding-box proximity and then
routed to the correct pin by geometry, which handles endpoints that land inside a
component box but far from its pin. A dead-end rescue gives a wire anchored on one
pin a longer directional reach toward a pin on a different component, recovering
strokes the detector cut short. Tolerances are expressed as multiples of the
median component size so a single rule spans the wide scale range of hand drawings.

\paragraph{Phase 2 --- degree-budget completion.}
After the base join, a non-inert component terminal whose net touches only its own
component is \emph{floating}: it is the signature of a wire the detector missed
entirely, which the base join cannot recover because no stroke connects it.
Ground (gnd), text, junction, and other single-terminal or non-conductive classes
are excluded from this notion. Each floating terminal is treated as a unit demand
to be satisfied by at most one new edge. Candidate completion edges are generated
to pins on \emph{other} components within a reach of $2.5\,\tau_{\mathrm{pin}}$,
excluding pins already on the terminal's net; the cost of an edge prefers a
geometric witness (an actual wire whose two ends lie near the two pins) and falls
back to pure Euclidean distance when no witness exists, so that genuinely dropped
wires can still be completed. The resulting bipartite problem --- floating
terminals against candidate target pins, each target offering up to three slots so
that legitimate multi-terminal nets are not starved --- is solved as a
minimum-cost assignment with the Hungarian algorithm \cite{Kuhn1955}, with a
per-terminal opt-out so that a terminal with no good target is left unconnected
rather than forced. The chosen matches are applied with a \emph{self-loop guard}:
a match that would merge two nets already sharing a component is skipped, so a
two-terminal part can never be shorted onto a single net.

This degree budget is what makes the method safe. Because every floating terminal
contributes at most one edge and the guard forbids self-loops, the completion
recovers dropped connections without the all-to-all over-merging that shorts dense
or bridge-like layouts. Base-join wire indices are carried onto the final nodes so
that downstream simulation and current visualization retain wire-level provenance;
completion edges are inferred and carry no wire, exactly as a manually drawn
connection would.

\subsection*{SPICE generation}

Each electrical node becomes a SPICE \cite{Nagel1973} node and each simulatable component
(resistor, capacitor, inductor, diode, voltage source, and similar) becomes a
device line; a ground node is mapped to node~0 when present. The emitted deck is
run through \texttt{ngspice} for a DC operating-point analysis, yielding node
voltages and device currents that are surfaced in the interface.

\subsection*{Synthetic ground-truth evaluation}

Because the real set has no net-level ground truth, the join is also evaluated on
a synthetic harness that runs the loop in the opposite direction. A small catalog
of circuits with known netlists is authored; each is laid out as a coordinate map
of component boxes and wire segments of the same form the detector produces;
detector-style error (endpoint jitter, cut-short truncation, dropped wires,
wrong-pin snaps, and anchor displacement of 30--80~px) is injected at increasing
severities; and the \emph{real} join and SPICE generator are run on the perturbed
map and scored against the authored truth. Two signals are reported: a
component-connectivity F1 against the authored nets, and whether the recovered
circuit simulates to the authored operating point. The harness supplies net-level
truth by construction, doubles as a regression test (the clean, error-free map
must round-trip to F1 = 1.0), and --- by searching over candidate join algorithms
against this truth --- was the means by which the Degree-Budget Topology Join was
discovered and selected over alternatives. Its one caveat is that the injected
error model is a first-pass approximation rather than a calibrated model of the
real detector's failure distribution; it is therefore used as a robustness and
regression signal, with the real benchmark remaining the decisive setting.

\begin{figure}[H]
\centering
\resizebox{0.98\textwidth}{!}{%
\begin{tikzpicture}[
    font=\small,
    box/.style={rounded corners=4pt, very thick, minimum width=3.0cm, minimum height=1.25cm, align=center, inner sep=5pt},
    io/.style={box, draw=orange!85!black, fill=orange!10},
    det/.style={box, draw=blue!70!black, fill=blue!8},
    pre/.style={box, draw=purple!70!black, fill=purple!8},
    wire/.style={box, draw=green!50!black, fill=green!10},
    join/.style={box, draw=teal!70!black, fill=teal!10},
    sim/.style={box, draw=red!60!black, fill=red!8},
    arrow/.style={-{Latex[length=3mm,width=2mm]}, line width=1pt, draw=gray!75!black},
    group/.style={rounded corners=8pt, draw=#1!40, fill=#1!4, line width=0.8pt, inner sep=8pt},
    group/.default=blue
]
\node[io]  (input)  at (0,0)    {\textbf{Input}\\photographed\\schematic};
\node[det] (detect) at (3.8,0)  {\textbf{Component detection}\\YOLO26M-OBB\\(16 classes)};
\node[pre] (pre)    at (7.6,0)  {\textbf{Guided preprocessing}\\median occlusion\\+ ROI crop};
\node[wire](wirex)  at (11.4,0) {\textbf{Wire extraction}\\Sauvola $\to$ CCL\\$\to$ PCA endpoints};

\node[join](base)   at (3.8,-3) {\textbf{Endpoint-graph base}\\union-find + dead-end\\rescue};
\node[join](budget) at (7.6,-3) {\textbf{Degree-budget completion}\\float-pin demands +\\min-cost matching};
\node[sim] (spice)  at (11.4,-3){\textbf{SPICE export}\\\texttt{ngspice}\\DC operating point};
\node[io]  (output) at (15.0,-3){\textbf{Output}\\simulatable\\netlist};

\draw[arrow] (input) -- (detect);
\draw[arrow] (detect) -- (pre);
\draw[arrow] (pre) -- (wirex);
\draw[arrow] (wirex.south) -- ++(0,-0.85) -| (base.north);
\draw[arrow] (detect.south) -- ++(0,-0.5) -| (base.north);
\draw[arrow] (base) -- (budget);
\draw[arrow] (budget) -- (spice);
\draw[arrow] (spice) -- (output);

\begin{scope}[on background layer]
\node[group=blue, fit=(input)(detect)(pre)(wirex),
  label={[font=\bfseries\footnotesize, text=blue!60!black]north:Detection and wire extraction}] {};
\node[group=teal, fit=(base)(budget)(spice)(output),
  label={[font=\bfseries\footnotesize, text=teal!60!black]north:Degree-Budget Topology Join and simulation}] {};
\end{scope}
\end{tikzpicture}
}
\caption{CircuitDigitizer pipeline. A trained oriented detector localizes
components and guides occlusion and cropping; a deterministic Sauvola-based stage
extracts wire segments; the Degree-Budget Topology Join builds an endpoint graph
and then completes floating component terminals with a reach-bounded, self-loop-
guarded minimum-cost matching; and the connected netlist is exported as SPICE.}
\label{fig:architecture}
\end{figure}
