\begin{thebibliography}{00}

\bibitem{Thoma2021}
F. Thoma, J. Bayer, Y. Li, A. Dengel, A public ground truth dataset for handwritten circuit diagram images, in: International Conference on Document Analysis and Recognition, Springer, 2021.

\bibitem{Sauvola2000}
J. Sauvola, M. Pietik{\"a}inen, Adaptive document image binarization, Pattern Recognition 33 (2) (2000) 225--236.

\bibitem{Otsu1979}
N. Otsu, A threshold selection method from gray-level histograms, IEEE Transactions on Systems, Man, and Cybernetics 9 (1) (1979) 62--66.

\bibitem{Niblack1986}
W. Niblack, An Introduction to Digital Image Processing, Prentice-Hall, Englewood Cliffs, NJ, 1986.

\bibitem{Gatos2006}
B. Gatos, I. Pratikakis, S. J. Perantonis, Adaptive degraded document image binarization, Pattern Recognition 39 (3) (2006) 317--327.

\bibitem{Shafait2008}
F. Shafait, D. Keysers, T. Breuel, Efficient implementation of local adaptive thresholding techniques using integral images, in: Document Recognition and Retrieval XV, Vol. 6815, SPIE, 2008, 681510.

\bibitem{Su2013}
B. Su, S. Lu, C. L. Tan, Robust document image binarization technique for degraded document images, IEEE Transactions on Image Processing 22 (4) (2013) 1408--1417.

\bibitem{ZhangSuen1984}
T. Y. Zhang, C. Y. Suen, A fast parallel algorithm for thinning digital patterns, Communications of the ACM 27 (3) (1984) 236--239.

\bibitem{Lam1992}
L. Lam, S.-W. Lee, C. Y. Suen, Thinning methodologies: a comprehensive survey, IEEE Transactions on Pattern Analysis and Machine Intelligence 14 (9) (1992) 869--885.

\bibitem{DudaHart1972}
R. O. Duda, P. E. Hart, Use of the Hough transformation to detect lines and curves in pictures, Communications of the ACM 15 (1) (1972) 11--15.

\bibitem{Gioi2010}
R. Grompone von Gioi, J. Jakubowicz, J.-M. Morel, G. Randall, LSD: a fast line segment detector with a false detection control, IEEE Transactions on Pattern Analysis and Machine Intelligence 32 (4) (2010) 722--732.

\bibitem{Rachala2022}
R. R. Rachala, M. R. Panicker, Hand drawn electrical circuit recognition using object detection and node recognition, SN Computer Science 3 (3) (2022) 244.

\bibitem{Schaefer2021}
B. Sch{\"a}fer, M. Keuper, H. Stuckenschmidt, Arrow R-CNN for handwritten diagram recognition, International Journal on Document Analysis and Recognition 24 (1--2) (2021) 3--17.

\bibitem{Elyan2020}
E. Elyan, L. Jamieson, A. Ali-Gombe, Deep learning for symbols detection and classification in engineering drawings, Neural Networks 129 (2020) 91--102.

\bibitem{Lee2020}
D.-Y. Yun, S.-K. Seo, U. Zahid, C.-J. Lee, Deep neural network for automatic image recognition of engineering diagrams, Applied Sciences 10 (11) (2020) 4005.

\bibitem{Yang2024}
L. Yang, J. Wang, J. Zhang, H. Li, K. Wang, C. Yang, D. Shi, Practical single-line diagram recognition based on digital image processing and deep vision models, Expert Systems with Applications 238 (2024) 122389.

\bibitem{Hemker2024}
D. Hemker, J. Maalouly, H. Mathis, R. Klos, E. Ravanan, From schematics to netlists: electrical circuit analysis using deep-learning methods, Advances in Radio Science 22 (2024) 61--75.

\bibitem{MorenoGarcia2024}
L. Jamieson, C. F. Moreno-Garc{\'i}a, E. Elyan, A review of deep learning methods for digitisation of complex documents and engineering diagrams, Artificial Intelligence Review 57 (2024) 136.

\bibitem{Bradski2000}
G. Bradski, The OpenCV Library, Dr. Dobb's Journal of Software Tools (2000).

\bibitem{Rabby2019}
M. K. A. Rabby et al., A survey on hand drawn circuit diagram digitization: techniques, datasets and challenges, IEEE Access (2019).

\bibitem{Shen2023}
Y. Shen et al., Automatic circuit schematic recognition: A review, Engineering Applications of Artificial Intelligence 126 (2023).

\bibitem{UltralyticsYOLO}
Ultralytics, Ultralytics YOLO documentation, 2024. \url{https://github.com/ultralytics/ultralytics} (accessed 2026-05-25).

\end{thebibliography}
